\mytitile\\~

### 2019-09-30 document.tex
Added authors, added main scheme

\usepackage{graphicx}% Include figure files
%\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage{lipsum}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{xparse}
\usepackage{bbm}
%\usepackage{multirow}
%\usepackage{makecell}
\graphicspath{{Pictures/}}
\begin{document}
	\preprint{AIP/123-QED}

	\title[Multiphoton transition and  Autler-Townes splittings in a strongly coupled double transmon system]{Multiphoton transition and  Autler-Townes splittings in a strongly coupled double transmon system\\~}

@@

	\author{A.V. Ustinov}
	\affiliation{ 
		Russian Quantum Center, Skolkovo village, Russia
	}%
	\affiliation{%
		Karlsruhe Institute of Technology, Karlsruhe, Germany
	}%

@@

>>>>

\usepackage{graphicx}% Include figure files
%\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage{lipsum}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{xparse}
\usepackage{bbm}
%\usepackage{multirow}
%\usepackage{makecell}
\graphicspath{{Pictures/}}

\newcommand{\mytitile}{Effects of intense light-matter interaction in a superconducting artificial molecule}
\begin{document}
	\preprint{AIP/123-QED}

	\title[\mytitile]{\mytitile\\~}

@@

	\author{V.B. Yursa}
	\affiliation{ 
		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia
	}%

	\author{A. Efimov}

	\affiliation{ 
		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia
	}%

	\author{K. Shiyanov}

	\affiliation{ 
		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia
	}%

	\author{O.V. Astafiev}
	\affiliation{ 
		Moscow Institute of Physics and Technology, Dolgoprundiy, Russia 
	}%

@@

\begin{figure*}
	\centering
	\includegraphics[width=.9\linewidth]{main_scheme}
	\caption{Explaining the origin of the AT satellites. \textbf{(a)} System level structure at 3.65 mA. At this current, the first transmon (orange) is below the second one (blue) exactly by $\alpha/2$ ($\omega_2 - \omega_1 = \alpha/2$), and thus $E_{02} - E_{10} = \hbar\omega_1$. Since $E_{12} - E_{02} = \omega_1$ as well, both $00\rightarrow 10$, two-photon $00 \rightarrow 02/2$ and three-photon $00\rightarrow 12/3$ transitions can occur around the same frequency of $\omega_1$. During the two-tone spectroscopy, the first transmon is driven by a strong signal of amplitude $\Omega_1$ (possibly, at a small detuning $\Delta_1$ from $\omega_1$ shown in green). The transmon-transmon interaction in RWA conserves the number of excitations and is depicted as orange-blue circles. \textbf{(b)} Moving to the frame rotating with the drive of the first transmon, we make all the states $\ket{0j},\ket{1j}$ nearly degenerate (in fact, now the first transmon splitting equals $\Delta_1$). However, the presence of a strong excitation lifts the degeneracy and the splitting changes to $\Omega_1^R = \sqrt{\Omega_1^2 + \Delta_1^2}$ (the first transmon becomes light-dressed). \textbf{(c)} Transitions in the light-dressed system when the second qubit is excited (level subspaces coupled by the corresponding drive operator are shown as blue ellipses). In the left part of the panel, all possible two-photon transitions near $\omega_1$ are depicted. The structure of the levels gives rise to three cases: the green transitions are not shifted in frequency, the orange are red-shifted by $\Omega_R^1/2$ and the blue are blue-shifted by $\Omega_R^2/2$. However, as shown in the right part of the panel, without the transmon-transmon interaction the satellite transitions are forbidden due the selection rule: $\bra{a,j}\hat{\mathbbm{1}}\otimes \hat n_2 \ket{b, j+1} = 0$ since $\braket{a}{b} = 0$. When the coupling equals $J$, the dispersive approximation yields $\bra{a,j}\hat{\mathbbm{1}}\otimes \hat n_2\ket{b, j+1}\propto J^2/(\omega_1-\omega_2)^2$ and the satellites may be observed.}
\end{figure*}
